---
title       : Titration-curve simulation for single-site binding systems
subtitle    : 
author      : Chao
job         : 
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : [mathjax]            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---

## Background

In biological studies, it's often to see simple 1:1 binding systems, e.g. binding of a receptor P to a ligand L forming a PL complex as shown below.

<div style='float:left'> <img src=./binding.png> </div>

<div style='font-size:80%'>
  <br><br>
  Such a system can be described by the following equations:  
  $$ L_{total} = L + PL $$
  $$ P_{total} = P + PL $$
  $$ Kd = (P*L) / PL $$
  $$ Bound = PL / P_{total} $$
  Note: P, L, and PL denote concentrations of the corresponding molecules.
</div>

---

## Background cont.

It's often that $L_{total}$ ,$P_{total}$ and Bound are known, while Kd is a constant to be determined. To do so:  
1. Usually a ligand L is gradually added into a protein solution (with a fixed concentration $P_{total}$)  
2. Bound is measured at different $L_{total}$ concentrations ($L_{total} / P_{total}$ ratio, or L/P ratio is often used instead).  
3. Data are fitted to the equations to get the constant Kd.

The first step for performing this type of so called "titration" experiments is often to simulate the system of interest with estimated parameters to determined experiment conditions.

Thus I have made this Shiny app to performed this kind of titration curve simulation for 1:1 binding systems. With user-provided parameters ($P_{total}$, final L/P ratio, and estimated Kd), the app can generate simulated titration curves (Bound vs L/P ratio) for two given systems for comparison.

---

## Example input and output

For example, system 1 has a $P_{total}$ of 100 uM and a Kd of 1 uM, while system 2 has a $P_{total}$ of 100 uM and a Kd of 10 uM; if we add ligand L gradually to a final L/P ratio of 2, then the app will generate the following simulated titration curves:

```{r eval=FALSE}
getdata <- function (pt,kd,lx){
  lp=seq(0,lx,length.out = 100); lt=lp*pt
  fr=((kd+pt+lt)-((kd+pt+lt)^2-4*pt*lt)^0.5)/(2*pt)
  data.frame(lp,fr) }

d1=getdata(100,1,2); d2=getdata(100,10,2)
da=merge(d1,d2,by='lp'); names(da)=c('L/P Ratio','Bound-1','Bound-2')

library(googleVis)
pars=list(width=1000,height=500,legend='right', hAxis="{title:'L/P Ratio'}",
          vAxis="{title:'Fraction Bound'}", colors="['red','blue']" )
G=gvisLineChart(da,options=pars); print(G,"chart")
```

---

## Example input and output cont.

```{r echo=FALSE,results="asis"}
getdata <- function (pt,kd,lx){
  lp=seq(0,lx,length.out = 100); lt=lp*pt
  fr=((kd+pt+lt)-((kd+pt+lt)^2-4*pt*lt)^0.5)/(2*pt)
  data.frame(lp,fr) }

d1=getdata(100,1,2); d2=getdata(100,10,2)
da=merge(d1,d2,by='lp'); names(da)=c('L/P Ratio','Bound-1','Bound-2')

library(googleVis)
pars=list(width=1000,height=500,legend='right', hAxis="{title:'L/P Ratio'}",
          vAxis="{title:'Fraction Bound'}", colors="['red','blue']" )
G=gvisLineChart(da,options=pars); print(G,"chart")
```
